Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-13 manuscript/manuscript.tex
Small changes in manuscript
Modifications in manuscript: improvements in Exponential Density

From every $D$ and $\delta$ combination we want to find the one that 
produces a numerical error lower than the 0.1\% threshold while keeping 
an effective computation, i.e. the ($D$, $\delta)$ pair that produces 
the minimum number of discretizations that ensure an acceptable 
numerical precision.
We can propose an heuristic method to perform this task: compute the 
numerical error for every ($D$, $\delta$) points belonging to a grid on 
the $D$, $\delta$ space and specify the pair that combines an 
acceptable numerical error with an efficient computation.

Because the algorithm is intended to work with default $D$ and $\delta$ 
values that ensures these two conditions for every density function, 
the default value for $D$ cannot be lower than the one determined for 
the linear function.
That's why we can only choose the ($D$, $\delta$) points on which
$D \geq D_\text{linear}$.
In this way we can divide the $D$, $\delta$ space in two subregions: 
one with $D < D_\text{linear}$ and other with $D \ge D_\text{linear}$.
The former contains points not eligible, while the latter one will 
contain the one that we want to find.

From the latter subregion we can explore the numerical error of points 
with $D = D_\text{linear}$ and different values of $\delta$.
We will call $\delta_p$ as the maximum $\delta$ at which the numerical 
error is lower than the 0.1\% threshold while keeping
$D = D_ \text{linear}$.
Greater $\delta$ values than $\delta_p$ will produce computations 
with high error, while lower $\delta$ values than $\delta_p$ will 
produce more discretizations leading to non-efficient computation.

@@

It worth mention that a greater $D$ or a lower $\delta$ 
increases the number of discretizations of the tesseroid.
Although a greater $D$ may subdivide it in the latitude, longitude 
and/or radial direction; a lower $\delta$ will only discretize the 
original tesseroid in the radial direction.
From this analysis we can conclude that a decrease in $\delta$ will 
produce a more efficient computation than an increase in $D$.

@@

On the other hand, the numerical error of points with $\delta > 
\delta_p$ can either be lower or greater than 0.1\%.
Any point in this subregion with acceptable numerical error will 
produce more discretizations than the ($D_\text{linear}$, $\delta_p$) 
point, due to $D$ value is increased.

>>>>

From every $D$ and $\delta$ combination we want to find the one that 
produces a numerical error lower than the 0.1\% threshold while keeping 
an effective computation, i.e. the ($D$, $\delta)$ pair that produces 
the minimum number of discretizations and ensures an acceptable 
numerical precision.
We can propose an heuristic method to perform this task: compute the 
numerical error for every ($D$, $\delta$) points belonging to a grid on 
the $D$, $\delta$ space and specify the pair that combines an 
acceptable numerical error with an efficient computation.

Because the algorithm is intended to work with default $D$ and $\delta$ 
values that ensures these two conditions for every density function, 
the default value for $D$ cannot be lower than the one determined for 
the linear function.
That's why we can only choose the ($D$, $\delta$) points on which
$D \geq D_\text{linear}$.
In this way we can divide the $D$, $\delta$ space in two subregions: 
one with $D < D_\text{linear}$ and other with $D \ge D_\text{linear}$.
We can ignore points belonging to the former one and focus on the 
latter.

From the $D \ge D_\text{linear}$ subregion we can explore the numerical 
error of points with $D = D_\text{linear}$ and different values of 
$\delta$.
We will call $\delta_p$ as the maximum $\delta$ at which the numerical 
error is lower than the 0.1\% threshold while keeping
$D = D_ \text{linear}$.
Greater $\delta$ values than $\delta_p$ will produce computations 
with high error, while lower $\delta$ values than $\delta_p$ will 
produce more discretizations leading to non-efficient computation.

@@

It worth mention that a greater $D$ or a lower $\delta$ 
increases the number of discretizations of the tesseroid.
Although a greater $D$ may divide it in the latitude, longitude 
and/or radial direction; a lower $\delta$ will only discretize the 
original tesseroid in the radial direction.
This means that a decrease in $\delta$ will produce a more efficient 
computation than an increase in $D$.
\todo{Should we keep this paragraph? The same is explained bellow.}

@@

On the other hand, we have no a priori information about the numerical 
error of points with $\delta > \delta_p$.
Although, if we find a point with acceptable numerical error in this 
region, we know it will produce more discretizations than the 
($D_\text{linear}$, $\delta_p$) point.
This is due to the fact that even an increase in $\delta$ will produce 
less density-based discretizations, the increase in $D$ will introduce 
even more subdivisions not only in the radial direction, but 
also in the latitude and logitude ones.
